Viscous Erosion in Porous Media

### 2018-03-15 docs/methods/erosion_methods.tex
Abstract

\begin{abstract} 
We consider two dimensional eroding bodies in Stokes flow
\end{abstract}

>>>>

\begin{abstract} 
We develop numerical methods to simulate the fluid-mechanical erosion of many bodies (order 50) in 2D Stokes flow. The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with resolution at the grain scale. Our fluid solver is based on a boundary-integral formulation of the Stokes equations. We solve the associated linear system iteratively with GMRES and use the fast-multipole method (FMM) to accelerate the matrix-vector products.

To evolve individual grains according to shear-driven erosion in a numerically stable manner, we regularize interface motion through curvature-penalization.

%{\thL} method, which allows us to regularize 
\end{abstract}
